Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-07-31 grove-paper.tex
Updates from Overleaf

@@

\begin{figure}
\[
\arraycolsep=0pt
\begin{array}{rlll}
 p    & {}\in Pat & {}\mathrel{::=}{} & x \mid \_ \\
 e    & {}\in Exp & {}\mathrel{::=}{} & \lambda p\mathord{:}\tau.e \mid e~e \mid e + e \mid n \mid \_ \\
 \tau & {}\in Typ & {}\mathrel{::=}{} & \tau \rightarrow \tau \mid Num \mid \_
\end{array}
\]
\caption{Formal syntax (as a grammar) for the lambda calculus that we are considering.}
\label{fig:formal-syntax}
\end{figure}

@@

$\K = \{ \Root, \ExpVar, \ExpLam, \ExpApp, \ExpNum, \ExpPlus,$

$\qquad\ \ \PatVar, \TypNum, \TypArrow \}$

$\I = \{ \Root, \LamParam, \LamType, \LamBody, \AppFun, \AppArg,$

$\qquad\ \ \PlusLeft, \PlusRight, \ArrowArg, \ArrowResult \}$

\vspace{2ex}

$\arity : \K \rightarrow \wp(\I)$

\vspace{2ex}

\begin{tabular}{ll}
    $\K$ & $\wp(\I)$ \\
    \hline
    $\Root$ & $\{ \Root \}$ \\
    $\ExpLam$ & $\{ \LamParam, \LamType, \LamBody \}$ \\
    $\ExpApp$ & $\{ \AppFun, \AppArg \}$ \\
    $\ExpPlus$ & $\{ \PlusLeft, \PlusRight \}$ \\
\end{tabular}

>>>>

\begin{figure}
\[
\arraycolsep=0pt
\begin{array}{lrlll}
 \textrm{Patterns:}          & p    & {}\in Pat & {}\mathrel{::=}{} & x \mid \_ \\
 \textrm{Expressions:\qquad} & e    & {}\in Exp & {}\mathrel{::=}{} & x \mid \lambda p\mathord{:}\tau.e \mid e~e \mid e + e \mid n \mid \_ \\
 \textrm{Types:}             & \tau & {}\in Typ & {}\mathrel{::=}{} & \tau \rightarrow \tau \mid Num \mid \_ \\
\end{array}
\]
\caption{Syntax as a grammar for the lambda calculus that we are considering.}
\label{fig:Syntax as a grammar}
\end{figure}

@@

The language we are modeling is shown in Figure~\ref{fig:Syntax as a grammar}.
Standard for a simply-typed lambda calculus except that
all terms have holes (represented by $\_$)
and the argument to a lambda is its own term.
The latter of which allows us to express lambdas with a hole for the bound variable.

In order to model this we define

@@

\begin{figure}
\[
\arraycolsep=0pt
\begin{array}{ll}
 \arity : \K \rightarrow & \wp(\I) \\
 \hline
 \arity(\Root)={}     & \left\{ \Root \right\} \\
 \arity(\PatVar)={}   & \left\{ \right\} \\
 \arity(\ExpVar)={}   & \left\{ \right\} \\
 \arity(\ExpLam)={}   & \left\{ \LamParam, \LamType, \LamBody \right\} \\
 \arity(\ExpApp)={}   & \left\{ \AppFun, \AppArg \right\} \\
 \arity(\ExpPlus)={}  & \left\{ \PlusLeft, \PlusRight \right\} \\
 \arity(\TypArrow)={} & \left\{ \ArrowArg, \ArrowResult \right\} \\
 \arity(\TypNum)={}   & \left\{ \right\} \\
\end{array}
\]
\caption{Constructors, Indexes and Arity}
\label{fig:Constructors, Indexes and Arity}
\end{figure}
